%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {Valador, Inc. (supporting NASA Office of the Chief Information Officer)} % Organization
    {Houston, TX} % Location
    {Mar. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prototype and deliver data analytics and visualization products ranging from regression models to natural language processing and data visualization.}
        \item {Give presentations and talks to further agency-wide knowledge-sharing and capabilities}
        \item {Plan and facilitate meetings and conversations about innovation and technology}
        \item {Co-supervise interns and manage a center-wide collaboration space}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Urbana Registration Analyst} % Job title
    {Intervarsity Christian Fellowship/USA} % Organization
    {Madison, WI} % Location
    {May 2015 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and distributed reports and audits for a conference with 16,000 registrants}
        \item {Used SQL scripts and vba macros to streamline and automate report analysis and distribution}
        \item {Managed and tracked over \$800,000 in discount and scholarship distribution}
        \item {Provided data-driven recommendations for shift-scheduling and other decisions}
        \item {Trained and managed a team of technical solutions volunteers on-site}
      \end{cvitems}
    }


\end{cventries}

\cvsection{Internships and Research}


\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Data Analysis Intern} % Job title
    {Perspectives Study Program} % Organization
    {Pasadena, CA} % Location
    {Oct. 2014 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote SQL queries to obtain data requested by program staff}
        \item {Analysized and manipulated data in Microsoft Excel}
        \item {Used d3.js to visualize data}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Clinical Research Internship} % Job title
    {City of Hope Comprehensive Care Center} % Organization
    {Duarte, CA} % Location
    {Oct. 2014 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Dr. Sumanta Pal}
        \item {Created spreadsheets of data based on patient information}
        \item {Assisted with data analysis, interpretation, and manuscript preparation}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Technician} % Job title
    {California Institute of Technology} % Organization
    {Pasadena, CA} % Location
    {Oct. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Professor Julia Kornfield and Dr. Amy Fu}
        \item {Research objective: Understanding the mechanism of a ophthalmic theraputic, in collaboration with Allegro Ophthalmics}
        \item {Designed and implemented experimental cell culture protocols}
        \item {Established a bioinformatics data analysis pipeline using Python, bash, and R}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {California State University, Los Angeles} % Organization
    {Los Angeles, CA} % Location
    {Sept. 2013 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Professor Ji Yun Son and Professor James Rudd (CSULA)}
        \item {Research objective: understanding how to present general chemistry concepts to maximize understanding}
        \item {Investigate the relationship between the order of examples being presented and student learning}
        \item {Mentored and trained an undergraduate researcher}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Fellow} % Job title
    {California Institute of Technology} % Organization
    {Pasadena, CA} % Location
    {Jun. 2013 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Professor Julia Kornfield and Dr. Amy Fu (Caltech)}
        \item {Research objective: To design and implement at 3-D cell migration assay for hydrogel-encapsulated cells}
        \item {Established protocols for (1) determining viability of cells encapsulated in a gel (2) long-term visualization of cells encapsulated in a gel (3) assisting fibroblast proliferation in a heparin-based hydrogel.}
        \item {Established a protocol to characterize fibroblast migration in a heparin-based hydrogel}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {California State University, Los Angeles} % Organization
    {Los Angeles, CA} % Location
    {Jun. 2010 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Professor Yong Ba \(CSULA\) and Professor Julia Kornfield \(Caltech\) and Dr. Jeremy Wei \(Caltech\)}
        \item {Research objective: to synthesize and characterize a mucoadhesive hydrogel system for controlled-release drug delivery}
        \item {Established a protocol for syntehsizing a heterobifunctional poly(ethylene glycol) based block copolymer}
      \end{cvitems}

    }

%---------------------------------------------------------
\end{cventries}
