%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {Valador, Inc. (supporting NASA Office of the Chief Information Officer)} % Organization
    {Houston, TX} % Location
    {Mar. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prototype and deliver data analytics and visualization products ranging from regression models to natural language processing}
        \item {Give presentations and talks to further agency-wide knowledge-sharing and capabilities}
        \item {Consult with teams across the agency to to provide guidance on data analytics, machine learning, visualization, and data management}
        \item {Co-supervise interns and manage a center-wide collaboration space}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
  {Selected Projects}{}{}{}
  {
   \begin{cvitems}
    \item {Developed an internal domain classifier and concept extraction microservice (Python)}
    \item {Created regression models for human capital data (R)}
    \item {Created data visualizations of NASA mission metadata (d3.js)}
    \item {Gamified facilities planning and budgeting process (Javascript)}
    \item {Supervised interns to develop "smart workplace" analytics prototypes (Raspberry Pi, cloud computing, Flask microservices)}
   \end{cvitems}
  }
    
%---------------------------------------------------------
  \cventry
    {Urbana Registration Analyst} % Job title
    {Intervarsity Christian Fellowship/USA} % Organization
    {Madison, WI} % Location
    {May 2015 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and distributed reports and audits for a conference with 16,000 registrants}
        \item {Used SQL scripts and vba macros to streamline and automate report analysis and distribution}
        \item {Managed and tracked over \$800,000 in discount and scholarship distribution}
        \item {Provided data-driven recommendations for shift-scheduling and other decisions}
        \item {Trained and managed a team of technical solutions volunteers on-site}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Clinical Research Internship} % Job title
    {City of Hope Comprehensive Care Center} % Organization
    {Duarte, CA} % Location
    {Oct. 2014 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed data collection/curation from electronic health records systems.}
        \item {Assisted with data analysis, interpretation, and manuscript preparation}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Technician} % Job title
    {California Institute of Technology} % Organization
    {Pasadena, CA} % Location
    {Oct. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented experimental cell culture protocols}
        \item {Created a data analysis pipeline for high-throughput RNA-seq data (Python, bash, and R)}
      \end{cvitems}
    }
    
\end{cventries}

